Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS

### 2011-09-02 ms.tex
corrected a wrong argumentation in the B_lim section

In addition there are a few interesting remarks in order. (1) For the VERITAS limits, the hardest CR spectral indices are most constraining because of the tightest upper limits. The opposite is true for the {\em Fermi} upper limits which probe the region around the pion decay bump characterized by a shape parameter that depends inversely on the CR spectral index \citep{article:PfrommerEnsslin:2004b}.  (2) For a steeper magnetic decline (larger $\alpha_{B}$), the CR number density needs to be larger to match the observed radio emission profiles which would yield a higher gamma-ray flux so that the upper limits are more constraining. This implies tighter lower limits for $B_{0}$. However, the largest choice of $\alpha_B=0.7$, which represents a flux-freezing magnetic field, is possibly too steep in the outer parts as it neglects the contributions from turbulent dynamos in these dynamically active regions with vorticity injection at corrugated structure formation shocks
\citep{article:PfrommerJones:2011}. (3) Interestingly, in all cases, we use the 0.4$^{\circ}$ limit that is always most constraining for our choice of magnetic field configurations.  This is because we need a substantially increasing relative CR pressure profile to match the observed radio profiles (for a given magnetic realization); hence that CR realization produces a larger flux within 0.4$^{\circ}$ in comparison to the ``isobaric CR model'' assumption ($X_{\CR} = \rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more constraining; hence the constraints on $B_{0}$ get better for the larger integration area. Physically, this may be achieved by considering CR transport processes such as streaming which produces an increasing $X_{\CR}$-profile due to the larger available phase space in the outer cluster regions.

>>>>

In addition there are a few interesting remarks in order. (1) For the VERITAS limits, the hardest CR spectral indices correspond to the tightest limits on $B_0$. This is because for an upper limit of CRs around 1.6 TeV and a CR population with a softer spectral index (larger $\alpha$) there is a comparably larger fraction of CRs at 100 GeV available which inject more radio-emitting electrons. In order to reproduce the observed synchrotron emission, this allows for smaller magnetic fields. The opposite is true for the {\em Fermi} upper limits at 1 GeV which probe CRs around a pivot point of 8 GeV: a softer CR spectral index implies a comparably smaller fraction of CRs at 100 GeV and hence decreases the radio-emitting secondary electrons. Equivalently larger magnetic fields are needed to compensate this in order to match the observed synchrotron flux.  (2) For a steeper magnetic decline (larger $\alpha_{B}$), the CR number density needs to be larger to match the observed radio emission profiles which would yield a higher gamma-ray flux so that the upper limits are more constraining. This implies tighter lower limits for $B_{0}$. However, the largest choice of $\alpha_B=0.7$, which represents a flux-freezing magnetic field, is possibly too steep in the outer parts as it neglects the contributions from turbulent dynamos in these dynamically active regions with vorticity injection at corrugated structure formation shocks \citep{article:PfrommerJones:2011}. (3) Interestingly, in all cases, we use the 0.4$^{\circ}$ limit that is always most constraining for our choice of magnetic field configurations.  This is because we need a substantially increasing relative CR pressure profile to match the observed radio profiles (for a given magnetic realization); hence that CR realization produces a larger flux within 0.4$^{\circ}$ in comparison to the ``isobaric CR model'' assumption ($X_{\CR} = \rmn{const.}$) for which the 0.2$^{\circ}$ upper limits are more constraining; hence the
constraints on $B_{0}$ get better for the larger integration area. Physically, this may be achieved by considering CR transport processes such as streaming which produces an increasing $X_{\CR}$-profile due to the larger available phase space in the outer cluster regions.
